Citeopotamus

### 2012-12-08 paper/paper.tex
Paper should be donezo

The rest of the paper is laid out as follows. Section \ref{sec:contributions}
is about what we are contributing. The following section describes out testing
dataset. We then talk about our architecture we created to solve the problem.
Then we go into how we parse papers and discuss the methods for choosing the
best citation. Then we go into future work, related work, and lastly our
conclusion.

\section{Contributions}\label{sec:contributions}
Our contributions consist of a dataset to test new solutions and methods to
recommend citations given a location for a citation.

@@

\subsection{Scraper}
The scraper, written in python, extensively uses urllib2 and lxml.html. The
first task is to access a search landing page using urllib2. Each search result
page maintains 10 publications per page and links at the top
and bottom of the search page that lead to other search result pages. Each
publication located on a search result page is used as a root paper.
Each listing on the search result page contains metadata for the publication
listed such as title, author, and path to the HTML of the publication.
Since we are collecting this dataset programmatically, the HTML
version is easier to work with than a PDF version of the publication, which
would require OCR to extract text. Due to the structure of the page (which is
amazingly consistent), the HTML is parsed in the following sections:
\begin{itemize}
   \item Abstract
   \item Body sections and titles
   \item References
      \begin{itemize}
         \item Search pages for each references paper
         \item Pubmed page for each reference paper
         \item Abstract, Title, and Author for refererence paper from pubmed
      \end{itemize}
\end{itemize}

@@

\section{Evaluation}
To evaluate our system, we find the total number of references that we have successfully placed.

>>>>

This paper discusses our approach to this problem, as well as the dataset we
procured for this use. In section \ref{sec:dataset} we highlight our dataset,
where it came from and what it contains. Section \ref{sec:architecture} follows
up with how we designed the system, our method of collecting our dataset, and
how it is structured, while section \ref{sec:parsing} goes into detail of how
our system parses and understands the publication text. Section
\ref{sec:methods} describes our methods for predicting a citation and section
\ref{sec:eval} discusses our approach for evaluating our system. Our results
are shown in section \ref{sec:results}, section \ref{sec:future} is where we
talk about future work and we discuss related work in section
\ref{sec:related}. Finally, we conclude our work in section
\ref{sec:conclusion}.

@@

\subsection{Scraper}\label{sec:scrape}
The scraper, written in python, extensively uses urllib2 and lxml.html. The
first task is to access a search landing page using urllib2. Each search result
page maintains 10 publications per page and links at the top
and bottom of the search page that lead to other search result pages. Each
publication located on a search result page is used as a root paper.
Each listing on the search result page contains metadata for the publication
listed such as title, author, and path to the HTML of the publication.
Since we are collecting this dataset programmatically, the HTML
version is easier to work with than a PDF version of the publication, which
would require OCR to extract text. Due to the structure of the page (which is
amazingly consistent), the HTML is parsed in the following sections:
\begin{itemize}
   \item Abstract
   \item Body sections and titles
   \item References
      \begin{itemize}
         \item Search pages for each references paper
         \item Pubmed page for each reference paper
         \item Abstract, Title, and Author for refererence paper from pubmed
      \end{itemize}
\end{itemize}

@@

\section{Evaluation}\label{sec:eval}
To evaluate our system, we find the total number of references that we have successfully placed.
